High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-08-05 paper/main.tex
text updates, but still need to update release version and zenodo link

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at \href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}. The fMRI dataset collected by \cite{SimoEtal16} has been made publicly available at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}

>>>>

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}
and has been deposited in the Zenodo database under accession code
(link here).
The raw fMRI data are protected and are not available due to data
privacy laws. The processed fMRI dataset collected by \cite{SimoEtal16} has been made publicly available at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.
